Rethinking how students learn to design programs

### 2016-04-23 manuscript-body.tex
fix ligatures; wrap text

My analysis details the work of Rebecca, a female first-year electrical
engineering major. I focus specifically on Rebecca's code for finding
``one-stop'' flights, which the instructor defined as ``all pairs of
ﬂights that route the user between the departure and arrival airports
with exactly 1 stop (i.e., a one-connection ﬂight)'' (Flights Database
handout, 2012). The one-stop problem is particularly challenging. To
solve it successfully students' code must accept a user's choice of
airports and day, then stitch together routes that involve two separate
flights in a way that passes stringent constraints for acceptable
layover times.

>>>>

My analysis details the work of Rebecca, a female first-year electrical
engineering major. I focus specifically on Rebecca's code for finding
``one-stop'' flights, which the instructor defined as ``all pairs of
flights that route the user between the departure and arrival airports
with exactly 1 stop (i.e., a one-connection flight)'' (Flights Database
handout, 2012). The one-stop problem is particularly challenging. To
solve it successfully students' code must accept a user's choice of
airports and day, then stitch together routes that involve two separate
flights in a way that passes stringent constraints for acceptable
layover times.
